A Decentralized Pub/Sub System for Trusted Machine Economy

### 2020-05-12 paper.tex
Add DM architecture and smart contract

\subsection{Paper Organization}
The rest of this paper is organized as follows. In Section RELATED-WORK, some related work of decentralized data marketplace, distributed data storage and use cases of MAM are analyzed. In Section BACKGROUND, the architecture of our proposed decentralized data marketplace is illustrated. In Section ARCHI, the interactions of MAM and Ethereum Smart Contract in trading model is well explained. The analysis and improvement of MAM are given in Section MAM-EXP. In Section OFFLOAD, the security issues and methods of offloading MAM operations to brokers will be discussed carefully. Finally, we conclude the paper in Section CONCLUSION.

@@

\subsection{Participants}
There are three major roles in the decentralized data marketplace (Fig.~\ref{fig:system_design}).

\begin{itemize}
\item \textbf{Data Provider: }
Data providers generate and preserve streaming data, and are willing to provide streaming data to subscribers. Providers can use the subscription fee paid by subscribers to improve the quality of their service.
\item \textbf{Subscribers: }
Subscribers aspire to obtain streaming data to promote the value of their service. However, it is a significant challenge for most subscribers to collect the desired data by themselves, so they look to purchasing the streaming data from data providers.
\item \textbf{Broker: }
Brokers represent data providers and subscribers to perform blockchain computing tasks and are expected to have higher resource. The brokers are requested to handle the product launching and subscription process, and brokerage fees is charged in each process.
\end{itemize}

@@

\subsubsection{Ethereum Smart Contract}
The smart contract is a protocol for formulating agreement on a blockchain that provides verification and execution of the contract. The code in the smart contract can interact with other contracts, make decisions, store data and transfer cryptocurrency. All conditions and states established in the contract are transparent and enforceable. The appearance of smart contracts makes trading more flexible, and achieves more complex trading patterns in reality.

The Product Contract is used during the trading process, where Product Contract records all the details of data products, such as MAM channel's and endpoint's ID, blinded session key and data providers' DID Document address. Furthermore, data providers and subscribers exchange session keys through a Product Contract without involving brokers. Though this design may cost more in transaction fees than doing so off-chain, it is considered a better strategy to assure the profit of both providers and subscribers. The further details of key exchangement will be illustrated in Section~\ref{section:trading}.

\subsubsection{Blind Signature}
There is an inherent risk in revealing session keys to brokers since contents may be copied by brokers, which would result in data providers' losses. Therefore, a blind signature is used to prevent session key copying for such circumstances. A blind signature\cite{blindSig} is a form of digital signature where the message is first "blinded" by a random "blinding factor", then passed to a signer to sign. Fig.~\ref{fig:blind_signature} illustrates the steps of blind signature. The resulting message, along with the blinding factor, can be later verified with the signer's public key. In our system design, brokers would perform blind signatures during the process of adding new products for data providers, in order to send the secret key of the MAM channel to the smart contract without knowing it.

\begin{figure}[!t]
	\centering
	\includegraphics[width=2. in]{blind_signature}
	\caption{The scheme of blind signature.}
	\label{fig:blind_signature}
\end{figure}

RSA blind signature\cite{cryptoNote} is used in our research. The user chooses a random number $r$ and uses the signer's public key $e$ to generate a blinding factor $r^e$. To prevent the message $m$ from being known by the signer, the user sends blinding message $c$ to the signer instead of $m$.

\begin{equation}
C = r^e m
\end{equation}

The signer signs the blinding message with private key $d$.

\begin{equation}
S = C^d
\end{equation}

$S$ is the signer's signature of $C$. In RSA system, $ed$ is equal to 1. To remove the blinding factor, the user computes the following calculation.

\begin{equation}
\frac{S}{r}= \frac{C^d}{r} = \frac{(r^e m)^d}{r} = \frac{r^{ed} m^d}{r} = m^d
\end{equation}

The user gets $m^d$ which is the signer's signature of the message $m$. At the same time, the signer does not know $m$ and the session key is protected.

>>>>

\subsection{Paper Organization}
The rest of this paper is organized as follows. In Section BACKGROUND, the architecture of our proposed decentralized data marketplace is illustrated. In Section RELATED-WORK, some related work of decentralized data marketplace, distributed data storage and use cases of MAM are analyzed. In Section ARCHI, the interactions of MAM and Ethereum Smart Contract in trading model is well explained. The analysis and improvement of MAM are given in Section MAM-EXP. In Section OFFLOAD, the security issues and methods of offloading MAM operations to brokers will be discussed carefully. Finally, we conclude the paper in Section CONCLUSION.

\section{Background}
In this section, we review the architecture of decentralized data marketplace and the two key components, Ethereum Smart Contract and MAM.

\subsection{Participants in Decentralized Data Marketplace}
There are three major roles, data providers, data consumers and brokers in the decentralized data marketplace which is similar to the pub/sub messaging model. But unlike the standard pub/sub model where brokers link the publishers and subscribers who are not aware of each others, in our proposed architecture, the brokers are only responsible for message delivery and essential verification processes. Fig.~\ref{fig:system_design}

\begin{itemize}
\item \textbf{Data Provider: }
Data providers can either generate, filter ,or process streaming data. The price of data products can They can make use of subscription fee that earned via trading for maintaining the equipment and improving the quality of data.
\item \textbf{Data Consumer: }
Data consumers are entities that are willing to buy data streams or high quality data sets. As data streams can be used in various applications and researches, it is hard to collect data from scratch. Thus, purchase is the fastest way to reach the goal. 
\item \textbf{Broker: }
Brokers are responsible for building agreement between data providers and consumers. Also brokers can represent data providers to perform computing tasks as brokers are expected to have higher resource. 
\end{itemize}

\subsection{Ethereum Smart Contract}
Ethereum is a cryptocurrency building on top of a public blockchain-based distributed ledger. It also provides a decentralized virtual machine that can perform the smart contract which is written by turing complete scripting
language.

The smart contract is a protocol for formulating agreement on a blockchain that provides verification and execution of the contract. The code in the smart contract can interact with other contracts, make decisions, store data and transfer cryptocurrency. All conditions and states established in the contract are transparent and enforceable. The appearance of smart contracts makes trading more flexible, and achieves more complex trading patterns in reality.

% to be removed
The Product Contract is used during the trading process, where Product Contract records all the details of data products, such as MAM channel's and endpoint's ID, blinded session key and data providers' DID Document address. Furthermore, data providers and subscribers exchange session keys through a Product Contract without involving brokers. Though this design may cost more in transaction fees than doing so off-chain, it is considered a better strategy to assure the profit of both providers and subscribers. The further details of key exchangement will be illustrated in Section~\ref{section:trading}.

@@

@@
